---
title: "p8105_hw3_yj2686"
author: "Yiqun Jin"
date: "10/16/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

**Load instacart dataset**

```{r}
data("instacart")
```


Description of instacart dataset:

The instacart dataset is an anonymized dataset with over 3 million online grocery orders from more than 200,000 Instacart users. This dataset contains `r nrow(instacart)` observations of products from online orders, and `r ncol(instacart)` variables which are `r names(instacart)`.

How many aisles are there, and which aisles are the most items ordered from?

There are `134` aisles and the most items ordered from `fresh vegetables`

```{r}
instacart %>% 
  group_by(aisle_id, aisle) %>%
  summarize(count = n()) %>%
  arrange(desc(count))
```

Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r fig.width=9,fig.height=9}
instacart %>% 
  count(aisle) %>% 
  rename(ordered_num = n) %>% 
  filter(ordered_num > 10000) %>% 
  mutate(
    aisle = fct_reorder(aisle, ordered_num)
  ) %>% 
  ggplot(aes(x = ordered_num, y = aisle)) +
  geom_point() +
  scale_x_continuous(breaks = scales::pretty_breaks(ordered_num = 10)) +
  labs(
    title = "The number of items ordered in each aisle",
    x = "The number of items",
    y = "Aisles",
    caption = "Data from instacart dataset"
  ) 
```

Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits” and the number of times each item is ordered.

```{r}
instacart %>% 
  filter(aisle == c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  rename(ordered_times = n) %>% 
  mutate(rank = min_rank(desc(ordered_times))) %>% 
  filter(rank < 4) %>% 
  relocate(aisle, rank) %>% 
  arrange(aisle, rank) %>% 
  knitr::kable()
```

Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week:

```{r}
instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  mutate(order_dow = ifelse(order_dow == 0, "Sunday", order_dow),
         order_dow = ifelse(order_dow == 1, "Monday", order_dow),
         order_dow = ifelse(order_dow == 2, "Tuesday", order_dow),
         order_dow = ifelse(order_dow == 3, "Wednesday", order_dow),
         order_dow = ifelse(order_dow == 4, "Thursday", order_dow),
         order_dow = ifelse(order_dow == 5, "Friday", order_dow),
         order_dow = ifelse(order_dow == 6, "Saturday", order_dow)) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  ) %>% 
  knitr::kable()
```
  
## Problem 2

**Load BRFSS dataset**

```{r}
data("brfss_smart2010")
```

**Data Cleaning**

```{r}
brfss_df = brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  separate(locationdesc, into = c("state", "location"), sep = ' - ') %>% 
  filter(topic == c("Overall Health")) %>% 
  mutate(response = factor(response, levels = c("Poor", "Fair", "Good", "Very good", "Excellent"),ordered = TRUE)) %>% 
  arrange(response) %>% 
  select(-locationabbr)
  ##select(-locationabbr, -class, -topic,  -question, -c(confidence_limit_low:geo_location))
brfss_df %>% view()
```

1. In 2002, which states were observed at 7 or more locations? What about in 2010?

```{r}
brfss_2002 = brfss_df %>% 
  filter(year == 2002) %>% 
  group_by(state) %>% 
  distinct(location) %>% 
  count(state) %>% 
  filter(n >= 7)

brfss_2002
```

ANSWER: `r brfss_2002$state` were observed at 7 or more locations in 2002.

```{r}
brfss_2010 = brfss_df %>% 
  filter(year == 2010) %>% 
  group_by(state) %>% 
  distinct(location) %>% 
  count(state) %>% 
  filter(n >= 7)

brfss_2010
```

ANSWER: 
`r brfss_2010$state` were observed at 7 or more locations in 2010.

2. Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. 

```{r}
excellent_df = brfss_df %>%
  filter(response == "Excellent") %>% 
  group_by(state, year) %>% 
  summarize(mean_data_value = mean(data_value, na.rm = TRUE))

excellent_df
```

Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).

```{r fig.width = 10, fig.height = 10}
excellent_df %>% 
  ggplot(aes(x = year, y = mean_data_value, color = state)) +
  geom_line(alpha = .4, aes(group = state, color = state)) +
  geom_point(alpha = .4, aes(group = state, color = state)) +
  theme(axis.text.x = element_text(size = 10), legend.position = "right") +
  labs(
    title = "Average data value of Excellent responses over time in different states",
    x = "Year",
    y = "Mean data value of Excellent responses",
    caption = "Data from brfss_smart2010"
  )
```

3. Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.

```{r}
NY_distribution = brfss_df %>% 
  filter(year %in% c(2006, 2010),
         state == "NY") %>% 
  group_by(year, response) %>% 
  summarize(mean_dataValue = mean(data_value, na.rm = TRUE)) 

NY_distribution %>% 
  ggplot(aes(x = response, y = mean_dataValue, fill = response)) +
  geom_col(position = "dodge", binwidth = 2) +
  facet_grid(. ~ year) +
  labs(
    title = "Distribution of data value for responses among locations in NY State",
    x = "responses among locations in NY State",
    y = "Mean data value",
    caption = "Data from brfss_smart2010"
  )
```

