---
title: "p8105_hw3_yj2686"
author: "Yiqun Jin"
date: "10/16/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
data("instacart")

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Description of instacart dataset:

The instacart dataset is an anonymized dataset with over 3 million online grocery orders from more than 200,000 Instacart users. This dataset contains `r nrow(instacart)` observations of products from online orders, and `r ncol(instacart)` variables which are `r names(instacart)`.

How many aisles are there, and which aisles are the most items ordered from?

There are `134` aisles and the most items ordered from `fresh vegetables`

```{r}
instacart %>% 
  group_by(aisle_id, aisle) %>%
  summarize(count = n()) %>%
  arrange(desc(count))
```

Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}
instacart %>% 
  count(aisle) %>% 
  filter(n > 10000) %>% 
  mutate(
    aisle = fct_reorder(aisle, n)
  ) %>% 
  ggplot(aes(x = n, y = aisle)) +
  geom_point() +
  labs(
    title = "The number of items ordered in each aisle",
    x = "The number of items",
    y = "Aisles",
    caption = "Data from instacart dataset"
  )
```

